Distributed Web Mining of Ethereum

### 2018-07-17 results/latexSrc/response-letter.txt

Response Letter to Reviewer Comments

Overall comments: We thank the TPC committee for the constructive feedback provided on our paper. Our response to specific comments is provided below.

----------------------- REVIEW 1 ---------------------
PAPER: 23
TITLE: Distributed Web Mining of Ethereum
AUTHORS: Trishita Tiwari, David Starobinski and Ari Trachtenberg

----------- Overall evaluation -----------
The paper proposes, analyzes, and describes an implementation of a new open source web-based miner for the Ethereum cryptocurrency using a centralized server. The system makes a use of the WASM to achieve its relatively high hash rate. I really liked the use of WASM and the good analysis. But believe that there are some issues that should be addressed:

 - Web based cryptocurrency miners regardless of being opensource or proprietary, as suggested, already exist in the market for quite a while. The paper suggests that WebEth has better results because of design decisions and a choice of technology (Web Assembly). I would expect to see a comparison between WebEth and other popular web-based cryptocurrency miners to make evaluation easier.

Response: As we discuss in the paper, to our knowledge, there is only one main commercial (closed source) web crypto miner on the market, namely CoinHive for Monero. However, Monero uses a completely different PoW algorithm (Cryptonite), which is inherently different from Ethash. Hence, a direct comparison between WebEth and CoinHive would not be insightful.

 - Section 3 jumps straight into implementation. A design section that better explains the overall design of WebEth is missing. It would also help to breakdown 3.1 to different subsections and provide a specific one to WebEth miner.

Response: We have restructured Section 3 so it includes a general overview before delving into the details of the implementation. There are now three separate subsections, one for the lazy evaluation algorithm, one for the implementation, and the last one for the performance evaluation.

 - Did you consider allowing the server to notify the clients once a new valid hash was found? I would expect that with sufficiently large number of clients, this would have better performance than waiting for a timeout. Regardless, some analysis on the length of the timeout would be nice.

Response: This comment is well-taken. We now mention this issue in Section 6 as a possible area for future work.

 - How many nodes do I need to actually profit from mining ether these days?

Response:  We have now included a ball park estimate within Section 5.

 - Some popular websites have millions of daily visitors. How does the system perform with 10K/100K/1M miners? Does it require an entire set of servers to handle the requests? It seems very solvable but would be great to see a few words about scalability.

Response:  We added a sentence regarding scalability at the end of Section 3.2.

==== Minor issues ===
abstract - You are comparing implementations to a miner. miner probably should be "one" or "implementation"
Introduction -
- "...efficient validation (or mining) or cryptocurrency..." - remove (or mining), this is not the meaning of the term (And also conflicts with the description on 2.1).
- "Instead, WebEth employs an lazy approach to generating..." - a*, to generate*
- Fig 2 - Did you mean WebEth architecture?
Overall - Captions to figures would help to better understand them.
- Fig 8 is missing

Response: Thank you. We have fixed these typos.

----------------------- REVIEW 2 ---------------------
PAPER: 23
TITLE: Distributed Web Mining of Ethereum
AUTHORS: Trishita Tiwari, David Starobinski and Ari Trachtenberg

----------- Overall evaluation -----------
The paper considers the use of World Wide Web for mining cryptocurrencies. It proposes a  browser-
based distributed miner of the Ethereum cryptocurrency, WebEth. The design of WebEth is described in the paper together with the experimental evaluations of  two prototype implementations in JavaScript and WebAssembly. The paper presents also a couple of possible applications that a WWW based crypto-miner can be used.

The paper is well written and describes probably the first open-source web-based cryptominer. The paper also presents a possible of application of such a cryptominer.

As the paper explains WebEth uses lazy evaluation, as the time passes the buffer of the browser starts filling up and makes hash computations faster. The hash rate reaches its maximum steady-state only once the buffer in the browser is almost full, though. It would have been nice to discuss this in the context of the applications proposed and in the context of browser user behavior.

Response: We have added a brief discussion at the end of Section 3.3 about the buffer fill rate in the context of websites.

### 2018-07-17 results/latexSrc/main.tex
added few more comments

% 
% instead of saying lazy evaluation -- say how much time do we take 
% some quantification on how much time does it take to get 
% put challenges in introduction -- what does this make hard to solve? Put in the introduction. 
% intro, one line on contributions, and put challenges in the beginning. -- this will allow to motivate better (can use dag, say you will explaon)

% \para{application}: then application. Then a new para how our approach can be applied to the problem. Put the whole section at the end. Also put the references.

% Don't use quotes on very long sentences. 
% Put Javascrip Wasm section after Ethash. This section is too small. Do we really want it. 
% Talk about wasm in one place, not two.

% remove pseudocode.
% Have a section of ethereum and define what block header and hash. Also define target etc 
% dEFINE epoch early on. 
% called Cache in ethereum terminology. Mention that the size of the cache varies right 
% define lightweight and full node earlier.
% Say each DAG consists of nodes and pages. Explain what 
% Ads: talk about how our approach can be applied to

% our approach --
% how long -- our key contribution is to measure if this is viable to wait till the hash rate gets good. We need to mention this earlier. 
% remove `n'
% the video application. 
% Have a name. 
% its not clear that js was used. 
% have a para on js and webasm in our approach. 
% have the definitions before the claim. 
% use a different var for Hash and 
% put in the logs!!

% look at all citations -- at least there should be a year and conference. 
% more descriptive captions for figures.

% minimize the jargon
% experiments should reinforce what you say before.

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{float}
\usepackage{graphicx}
% \usepackage{balance}
% \usepackage{color}
\usepackage{makecell}
\usepackage{amsmath}
% \usepackage{algorithmic}
\usepackage{amssymb}
\usepackage{caption}
\newcommand{\trishita}[1]{}%{{\color{magenta}\bfseries[Trishita: #1]}}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $\blacksquare$}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\begin{document}
%
\title{Distributed Web Mining of Ethereum
% \thanks{Supported by organization x.}
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Trishita Tiwari%\orcidID{0000-1111-2222-3333} 
\and
David Starobinski%\orcidID{1111-2222-3333-4444} 
\and
Ari Trachtenberg%\orcidID{2222--3333-4444-5555}
}
%
\authorrunning{T. Tiwari et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Boston University, Department of Electrical and Computer Engineering, Boston, MA 02215, USA \\
\email{\{trtiwari,staro,trachten\}@bu.edu}}
%
\maketitle             
%
\begin{abstract}
We consider the problem of mining crytocurrencies by harnessing the inherent distribution capabilities of the World Wide Web. More specifically, we propose, analyze, and implement \verb|WebEth|, a browser-based distributed miner of the Ethereum cryptocurrency. \verb|WebEth| handles Proof-of-Work (PoW) calculations through individualized code that runs on the client browsers, and thereafter collates them at a web server to complete the mining operation. \verb|WebEth| is based on an lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server. We provide proofs-of-concept of \verb|WebEth| based on \verb|JavaScript| and \verb|WebAssembly| implementations, with the latter reaching hash rates up to roughly 40 kiloHashes per second, which is only 30\% slower than the corresponding native \verb|C++|-based miner.
Finally, we explore several applications of \verb|WebEth|, including monetization of web content, rate limitation to server access, and private Ethereum networks. Though several distributed web-based cryptominers have appeared in the wild (for other currencies), either in malware or in commercial trials, we believe that \verb|WebEth| is the first open-source cryptominer of this type.
% The process of legitimating cryptocurrencies (such as Bitcoin and Ethereum) is done
% through mining, often in a competitive and distributed manner by means of a small number of
% large, loosely-organized mining colonies following proprietary protocols.  We

% Cryptocurrencies such as Bitcoin and Ethereum are valdated and legitimated through mining,
% a competitive and often distri

% We propose and analyze an open-source platform for distributed cryptocurrency mining.

% Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities. This paper proposes a web browser based mining implementation for Ethereum implemented both in JavaScript and WebAssembly to perform the necessary Proof-of-Work (PoW) computations to mine the Ethereum blockchain. We explore a lazy evaluation based technique to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources. We obtain the best results with the WebAssembly implementation, with hash rates reaching upto 39651H/s ~\trishita{Not sure if we need such a specific number}, which, as we demonstrate, is merely 30.2\% slower than a native miner that uses the same algorithm for mining under the same conditions. We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.

\keywords{crypto-currency \and Ethereum \and distributed computing \and web-browser computing \and mining}
\end{abstract}
%
%
%
\section{Introduction}
Cryptocurrencies are increasingly gaining traction as a viable form of currency.  This has been accompanied by a correspondingly increasing interest in the efficient validation (or \emph{mining}) of cryptocurrency transactions.  Whereas initial efforts in this domain have focused on creating dedicated hardware for this task ~\cite{asics}, %AT - citation needed
\trishita{Add citation}
more recent approaches have examined repurposing existing infrastructure. Indeed, one such class of efforts has focused on the use of client web browsers as a platform for distributed computing~\cite{Cushing}. The growing popularity of CoinHive~\cite{coinhive} is a case in point of the potential success of distributed in-browser cryptocurrency mining as a commercial (if malicious) enterprise.

In this work, we propose \verb|WebEth|, a browser-based distributed miner for the popular Ethereum block chain~\cite{ethereum}. \verb|WebEth| tackles the challenge of achieving a profitable hash rate within a distributed ensemble of browsers under constrained memory, computation and network usage. Indeed, every browser needs to store a data structure of at least 1~GB in memory in order to mine Ethereum. Clearly, it is unfeasible to transfer this entire data structure every time a browser loads a web page. Instead, \verb|WebEth| employs an lazy approach to generating this data structure while mining. Through our experiments, we show that this approach takes at most five minutes to reach a steady state hash rate -- making it ideal for web applications where users spend time, such as gaming and video streaming. Our experiments also show that \verb|WebEth| yields a hashing rate of up to 40 kiloHashes/s, which, despite the overhead from running the algorithm in a browser, is only 30\% smaller than the performance of a corresponding miner running natively.

%\subsection{Our Contributions}
%In this work, we explore the web-based cryptocurrency mining of the popular Ethereum block chain, % %\trishita{Add citation}%AT - citation needed
%and propose a number of potential applications consequent to this platform.

The main contributions of this work are as follows:
\begin{itemize}
\item We propose \verb|WebEth| \cite{WebEth}, an open-source implementation of a distributed web-based Ethereum cryptominer in both \verb|JavaScript| and \verb|WebAssembly| that can operate under relatively resource constrained environments. Though miners for other currencies exist in the wild (e.g. CoinHive~\cite{coinhive}), they are all proprietary and closed-source.
\item We provide theoretical analysis and experimental evidence of the potential efficacy of the lazy approach adopted by \verb|WebEth| to achieve high hashing rates.
%\trishita{I feel like this next part is repetitive}Our miner employs an lazy approach to mining that takes $\approx$ 5 minutes for it to reach its maximum hash rate. In addition, we show that our \verb|WebAssembly| implementation can provide hash rates up to 40 kiloHashes/s, which is only 30\% smaller than the hash rate provided by a native C++ miner that employs the same algorithm.
\item We propose a number of potential applications built upon \verb|WebEth|, including rate-limiting server access, usage tracking, and content monetization.
\end{itemize}

% Our research involves providing implementations of a distributed, web browser based Ethereum miners in \verb|JavaScript| and \verb|WebAssembly|, and studying whether or not it is feasible for real world purposes. While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works involve crypto-currency mining. While CoinHive does perform distributed mining using web browsers, it is closed source, and also works with a different crypto-currency (Monero). Hence, we are pioneers in offering an open source architecture for Ethereum mining with web browsers. Our miner gives us a hashrate of about 39kH/s, which, given the versatility of the Ethereum framework, is useful and practical for many applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks, web content monetization, as discussed below.

% \subsection{Applications}

\paragraph{Related Work}
Distribution of a common task is hardly a new concept~\cite{scheduling,parallel,orca}, but the growing popularity and efficiency of dynamic web content and client-side scripting languages like \verb|JavaScript| and \verb|WebAssembly|
have made web browsers an enticing implementation option~\cite{WebFlow,Duda,Cushing}.  Coinhive~\cite{coinhive} has
built into this environment a proprietary method for mining the Monero cryptocurrency, but this is often done on
the browsers of unsuspecting users.  A more ethical, open-sourced alternative, the Basic Attention Token~\cite{basicAttentionToken}, is an Ethereum-based ERC20 token~\cite{erc20} currently in development to be used in conjunction with the Brave browser~\cite{BraveBrowser} to generate ad revenue for website publishers by \emph{measuring a user's attention} on an advertisement. This platform promises to balance the ties between website users, publishers, and advertisers to ensure that users get only ads they would accept, advertisers pay for actual users (instead of click bots), and publishers actually get revenue instead of begging users to turn off their ad blockers.

% So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling,parallel,orca}. Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems. As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow,Duda,Cushing}. 
% Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit. 
% In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate. This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software. 
% Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|. Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}. Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.

% One sees the growing popularity of distributed web computation through the recent development of increasingly popular Monero mining library CoinHive~\cite{coinhive}. In terms of the potential monetization aspect of the project, there exists an ethical alternative to CoinHive called the Basic Attention Token ~\cite{basicAttentionToken}. The Basic Attention Token is an ERC20 Token built on Ethereum that is used along with the Brave browser to generate Ad revenue for website publishers by measuring a user's attention span on an advertisement. Note that this is not a replacement for Ad revenue, but a platform to balance the ties between website users, publishers, and advertisers. It ensures that users get only ads they would accept, advertisers pay for actual users instead of click bots, and publishers actually get revenue instead of pleading the users to turn off their Ad blockers.

\paragraph{Roadmap}
The remainder of the paper is organized as follows. In Section 2\ref{sec:background} we cover the relevant background and related literature for our work.  In particular, we provide a self-contained description of Ethash, the Ethereum mining Proof-of-Work (PoW), and \verb|WebAssembly|, the language in which we implement an efficient miner. Section 3\ref{sec:webeth} describes \verb|WebEth|, including its lazy approach to distributing the Ethash PoW over numerous, resource-constrained browsers. This section also includes a performance analysis. We present the experimental results of our implementations in Section 4\ref{sec:results}. In Section 5\ref{sec:applications} we discuss several potential applications of our mining platform. We conclude in Section 6\ref{sec:conclusion}.

\section{Background}
\label{sec:background}
\subsection{Cryptocurrencies: a general overview}
Most cryptocurrencies like Ethereum involve storing transactions in blocks, and the entire history of transactions is collated in a data structure known as a block chain. The block chain is managed by dedicated machines called \emph{client nodes}; where each client node typically stores the entire block chain. However, because each client node operates on its own copy of the block chain, the block chains on different nodes may go out of sync. Hence, there needs to be an accepted mechanism to decide the order in which new transaction blocks are appended to this block chain. 
For this, every time a new transaction takes place, the transaction is pooled together with all other transactions that have been broadcasted to the network, but haven't been added to the block chain yet. For most currencies, the data structure that stores these unconfirmed transactions is known as the \emph{mem pool}. A miner picks valid transactions from his mem pool and creates a new block out of these transactions. Once this happens, the goal of the miner is to have his/her block appended to the block chain, which is achieved through a process called \emph{mining}.
% This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}. 
% Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''. 
Mining involves a race amongst miners to solve a \emph{Proof-of-Work} (PoW) puzzle, which is usually an energy intensive computation. The winner of this race gets to have his block appended to the block chain. The winner also receives a payout, which acts as an incentive to mine. 
% This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain. 
Ethereum uses Ethash as its PoW algorithm, which is explained in detail below.

@@

A \emph{block header} contains meta-data related to the transactions of the corresponding block, and it is provided as an input to the Ethash algorithm together with an integer \emph{nonce}.  The nonce is chosen in a brute-force fashion in order to hash, together with the block header, into a value that matches a specific pattern (based on a predefined \emph{difficulty threshold}). The process of finding an appropriate nonce for a given block is known as \emph{mining}.
%\item \textbf{Difficulty Threshold}: An integer value below which the hash digest output of Ethash should be in order for the miner to have successfully mined the block.

@@

An \emph{epoch} is a unit of ``time'' that spans 30,000 blocks.  All of the data structures in Ethash (mentioned below) need a 256 bit \emph{seed}, which differs for every epoch. For the first epoch the seed is a Keccak-256~\cite{keccak} hash of a series of 32 bytes of zeros. For every other epoch it is always the Keccak-256 hash of the previous seed hash.  The seed for a particular epoch is used to compute a data structure known as the \emph{Cache}, which is an array of 4 byte integers \cite{Ethmining}. The Cache production process involves using the seed hash to first sequentially fill up the Cache, then performing two passes of the RandMemoHash algorithm~\cite{randmemohash} on top of it to get the final Cache value. 
% This transforms the initial cache to give us the final value for the cache. 
Light weight clients may use this Cache for verifying hashes, while full node clients can use it to calculate a Directed Acyclic Graph (DAG) dataset, as described below.  A Ethereum \emph{Directed Acyclic Graph} is stored as a large byte array (around 1 GB in size on the private Ethereum Network used for our experiments) and has the following two attributes:
  \begin{enumerate}
  \item \emph{Node}: Each DAG node in this byte array spans 64 bytes, and node indices are therefore aligned at a 64 byte boundary.
  \item \emph{Page}: Each DAG page spans 2 nodes, however, page accesses are not aligned at a 2 node boundary. The mining process involves accessing some DAG pages and hashing them together with the block header and nonce.
  \end{enumerate}
Each node in the DAG is generated by combining data from 256 pseudo-randomly selected Cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG. Finally, intermediate byte arrays used to store temporary results in the Ethash algorithm are known as \emph{Mix}es.

@@

Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128-byte wide Mix, as seen in step 1 of Figure 1\ref{fig:ethash}. The Mix is then used to fetch a specific page of the DAG from memory. After this, the Mix is updated with the fetched page of the DAG (step 2). Then, this updated Mix is used to fetch a new page of the DAG (step 3). This process of sequentially fetching parts of the DAG is repeated 64 times (step 4), and the final value of the Mix is put through a transformation to obtain a 32 byte digest (step 5). This digest is then compared to the threshold (step 6). If it is smaller than the threshold, the nonce is valid and the block is successfully mined and can be broadcast to the network. However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce~\cite{Ethmining}.

% Below is the pseudo-code for the algorithm for completeness.\\
% \begin{algorithmic}[H]
% \label{miningAlgo}
% \STATE $mix \gets mixInit(\{header,nonce\})$
% \FOR{$i = 0;\;i < 64;\;i++$}
%   \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
%   \STATE $dagPage \gets DAG[dagPageIndex]$
%   \STATE $mix \gets updateMix(dagPage,mix)$
% \ENDFOR
% \STATE $digest \gets postProcessFunction(mix)$
% \IF {$digest <= targetThreshold$}
% 	\RETURN \TRUE
% \ENDIF
% \RETURN \FALSE
% \end{algorithmic}

@@

% This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin. GPU miners, however, do have an advantage, normally having hashrates of over 10 times that of a CPU miner.

@@

%\subsection{Challenges}
%The crux of having a good hashrate for Ethereum lies in having quick access to the DAG. One of the biggest challenges with mining on a distributed ensemble of browsers is to transfer and store this data structure within each worker browser. However, given that the DAG for an Ethereum network is at least 2 GB (and growing), transferring it to the browser every time a client loads our web page is impractical. Furthermore, even if one somehow manages to transfer the DAG to the client when the web page loads, the browser still has to store the DAG in memory, thereby using a sizeable amount of resources on the client machine. In section~\ref{sec:approach} we discuss approaches to tackle some of these challenges.

\section{WebEth}
\label{sec:webeth}
%\label{sec:approach}
%\subsection{Approach}
% \trishita{I think it would be nice if we show how we modified the algorithm shown in the previous section. I will add that over here}

\verb|WebEth| is based on a lazy evaluation to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers. Specifically, as soon as each browser connects to the webserver, the server sends to the browser the current header of the block being mined and the Cache. Once the browser receives the Cache, it allocates an array buffer to store the DAG node.
%s that fall between indices 0 and $N$ that will be computed in the future. (Note that the $N$ is a variable parameter reflecting the length of the buffer with which we experiment in our analysis). 
Once the buffer is allocated, the browser can start iterating over nonces to compute hashes.

Since, to begin with, the browser does not store any nodes of the DAG, it must compute each node on the fly using the Cache. However, every node that the browser computes is stored in the buffer, for quicker access in the future. Hence, as time passes, the buffer starts filling up, such that more and more nodes are quickly accessed from the buffer rather than being computed from the ground-up, which makes hash computations faster with time. This has the effect that the longer the user remains on the web-page, the better the hash rate gets for that user.

% Our modified algorithm is shown below:

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{float}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\newcommand{\trishita}[1]{}%{{\color{magenta}\bfseries[Trishita: #1]}}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $\blacksquare$}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\begin{document}
%
\title{Distributed Web Mining of Ethereum
}
\author{
Trishita Tiwari
\and
David Starobinski
\and
Ari Trachtenberg
}
%
\authorrunning{T. Tiwari et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Boston University, Department of Electrical and Computer Engineering, Boston, MA 02215, USA \\
\email{\{trtiwari,staro,trachten\}@bu.edu}}
%
\maketitle             
%
\begin{abstract}
We consider the problem of mining crytocurrencies by harnessing the inherent distribution capabilities of the World Wide Web. More specifically, we propose, analyze, and implement \verb|WebEth|, a browser-based distributed miner of the Ethereum cryptocurrency. \verb|WebEth| handles Proof-of-Work (PoW) calculations through individualized code that runs on the client browsers, and thereafter collates them at a web server to complete the mining operation. \verb|WebEth| is based on a lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server. We provide proofs-of-concept of \verb|WebEth| based on \verb|JavaScript| and \verb|WebAssembly| implementations, with the latter reaching hash rates up to roughly 40~kiloHashes per second, which is only 30\% slower than the corresponding native \verb|C++|-based implementation.
Finally, we explore several applications of \verb|WebEth|, including monetization of web content, rate limitation to server access, and private Ethereum networks. Though several distributed web-based cryptominers have appeared in the wild (for other currencies), either in malware or in commercial trials, we believe that \verb|WebEth| is the first open-source cryptominer of this type.

\keywords{crypto-currency \and Ethereum \and distributed computing \and web-browser computing \and mining}
\end{abstract}
%
%
%
\section{Introduction}
Cryptocurrencies are increasingly gaining traction as a viable form of currency.  This has been accompanied by a correspondingly increasing interest in the efficient validation of cryptocurrency transactions.  Whereas initial efforts in this domain have focused on creating dedicated hardware for this task ~\cite{asics}, more recent approaches have examined repurposing existing infrastructure. Indeed, one such class of efforts has focused on the use of client web browsers as a platform for distributed computing~\cite{Cushing}. The growing popularity of CoinHive~\cite{coinhive} is a case in point of the potential success of distributed in-browser cryptocurrency mining as a commercial (if malicious) enterprise.

In this work, we propose \verb|WebEth|, a browser-based distributed miner for the popular Ethereum block chain~\cite{ethereum}. \verb|WebEth| tackles the challenge of achieving a profitable hash rate within a distributed ensemble of browsers under constrained memory, computation and network usage. Indeed, every browser needs to store a data structure of at least 1~GB in memory in order to mine Ethereum. Clearly, it is unfeasible to transfer this entire data structure every time a browser loads a web page. Instead, \verb|WebEth| employs a lazy approach to generate this data structure while mining. Through our experiments, we show that this approach takes at most five minutes to reach a steady state hash rate -- making it ideal for web applications where users spend time, such as gaming and video streaming. Our experiments also show that \verb|WebEth| yields a hashing rate of up to 40 kiloHashes/s, which, despite the overhead from running the algorithm in a browser, is only 30\% smaller than the performance of a corresponding miner running natively.

The main contributions of this work are as follows:
\begin{itemize}
\item We propose \verb|WebEth| \cite{WebEth}, an open-source implementation of a distributed web-based Ethereum cryptominer in both \verb|JavaScript| and \verb|WebAssembly| that can operate under relatively resource constrained environments. Though miners for other currencies exist in the wild (e.g. CoinHive~\cite{coinhive}), they are all proprietary and closed-source.
\item We provide theoretical analysis and experimental evidence of the potential efficacy of the lazy approach adopted by \verb|WebEth| to achieve high hashing rates.
\item We propose a number of potential applications built upon \verb|WebEth|, including rate-limiting server access, usage tracking, and content monetization.
\end{itemize}

\paragraph{Related Work:}
Distribution of a common task is hardly a new concept~\cite{scheduling,parallel,orca}, but the growing popularity and efficiency of dynamic web content and client-side scripting languages like \verb|JavaScript| and \verb|WebAssembly|
have made web browsers an enticing implementation option~\cite{WebFlow,Duda,Cushing}.  Coinhive~\cite{coinhive} has
built into this environment a proprietary method for mining the Monero cryptocurrency, but this is often done on
the browsers of unsuspecting users.  A more ethical, open-sourced alternative, the Basic Attention Token~\cite{basicAttentionToken}, is an Ethereum-based ERC20 token~\cite{erc20} currently in development to be used in conjunction with the Brave browser~\cite{BraveBrowser} to generate ad revenue for website publishers by \emph{measuring a user's attention} on an advertisement. This platform promises to balance the ties between website users, publishers, and advertisers to ensure that users get only ads they would accept, advertisers pay for actual users (instead of click bots), and publishers actually get revenue instead of begging users to turn off their ad blockers.

\paragraph{Roadmap:}
The remainder of the paper is organized as follows. In Section \ref{sec:background} we cover the relevant background and related literature for our work.  In particular, we provide a self-contained description of Ethash, the Ethereum mining Proof-of-Work (PoW), and \verb|WebAssembly|, the language in which we implement an efficient miner. Section \ref{sec:webeth} describes \verb|WebEth|, including its lazy approach to distributing the Ethash PoW over numerous, resource-constrained browsers. This section also includes a performance analysis. We present the experimental results of our implementations in Section \ref{sec:results}. In Section \ref{sec:applications} we discuss several potential applications of our mining platform. We conclude in Section \ref{sec:conclusion}.

\section{Background}
\label{sec:background}
\subsection{Cryptocurrencies: a general overview}
Most cryptocurrencies like Ethereum involve storing transactions in blocks, and the entire history of transactions is collated in a data structure known as a block chain. The block chain is managed by dedicated machines called \emph{client nodes}; where each client node typically stores the entire block chain. However, because each client node operates on its own copy of the block chain, the block chains on different nodes may go out of sync. Hence, there needs to be an accepted mechanism to decide the order in which new transaction blocks are appended to this block chain. 
For this, every time a new transaction takes place, the transaction is pooled together with all other transactions that have been broadcasted to the network, but haven't been added to the block chain yet. For most currencies, the data structure that stores these unconfirmed transactions is known as the \emph{mem pool}. A miner picks valid transactions from his mem pool and creates a new block out of these transactions. Once this happens, the goal of the miner is to have his/her block appended to the block chain, which is achieved through a process called \emph{mining}.
Mining involves a race amongst miners to solve a \emph{Proof-of-Work} (PoW) puzzle, which is usually an energy intensive computation. The winner of this race gets to have his block appended to the block chain. The winner also receives a payout, which acts as an incentive to mine.

Ethereum uses Ethash as its PoW algorithm, which is explained in detail below.

@@

A \emph{block header} contains meta-data related to the transactions of the corresponding block, and it is provided as an input to the Ethash algorithm together with an integer \emph{nonce}.  The nonce is chosen in a brute-force fashion in order to hash, together with the block header, into a value that matches a specific pattern (based on a predefined \emph{difficulty threshold}). The process of finding an appropriate nonce for a given block is known as \emph{mining}.

@@

An \emph{epoch} is a unit of ``time'' that spans 30,000 blocks.  All of the data structures in Ethash (mentioned below) need a 256 bit \emph{seed}, which differs for every epoch. For the first epoch the seed is a Keccak-256~\cite{keccak} hash of a series of 32 bytes of zeros. For every other epoch it is always the Keccak-256 hash of the previous seed hash.  The seed for a particular epoch is used to compute a data structure known as the \emph{Cache}, which is an array of 4 byte integers \cite{Ethmining}. The Cache production process involves using the seed hash to first sequentially fill up the Cache, then performing two passes of the RandMemoHash algorithm~\cite{randmemohash} on top of it to get the final Cache value.

Light weight clients may use this Cache for verifying hashes, while full node clients can use it to calculate a Directed Acyclic Graph (DAG) dataset, as described below.  A Ethereum \emph{Directed Acyclic Graph} is stored as a large byte array (around 1 GB in size on the private Ethereum Network used for our experiments) and has the following two attributes:
  \begin{enumerate}
  \item \emph{Node}: Each DAG node in this byte array spans 64 bytes, and node indices are therefore aligned at a 64 byte boundary.
  \item \emph{Page}: Each DAG page spans 2 nodes, however, page accesses are not aligned at a 2 node boundary. The mining process involves accessing some DAG pages and hashing them together with the block header and nonce.
  \end{enumerate}
Each node in the DAG is generated by combining data from 256 pseudo-randomly selected Cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG. Finally, intermediate byte arrays used to store temporary results in the Ethash algorithm are known as \emph{Mix}es.

@@

Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128-byte wide Mix, as seen in step 1 of Figure \ref{fig:ethash}. The Mix is then used to fetch a specific page of the DAG from memory. After this, the Mix is updated with the fetched page of the DAG (step 2). Then, this updated Mix is used to fetch a new page of the DAG (step 3). This process of sequentially fetching parts of the DAG is repeated 64 times (step 4), and the final value of the Mix is put through a transformation to obtain a 32 byte digest (step 5). This digest is then compared to the threshold (step 6). If it is smaller than the threshold, the nonce is valid and the block is successfully mined and can be broadcast to the network. However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce~\cite{Ethmining}.

@@

@@

\section{WebEth}
\label{sec:webeth}
In this Section, we present our Web mining architecture for Ethereum. A diagram of the \verb|WebEth| architecture is depicted in Figure~\ref{fig:hybridArchitecture}. The architecture of the miner itself involves the browser connecting to a central node as soon as the web page loads (Steps 1 and 2 in Figure~\ref{fig:hybridArchitecture}). On connecting, the browser then receives the current block header hash and Cache (Step 3), using which it begins mining using the lazy evaluation algorithm discussed below (Step 4). Then, the browser could take one of two paths -- it could either have solved the block (Step 5a), in which case it sends the solution to the central node and asks for the next block to solve. Or it could timeout (Step 5b), in which case it polls the central node again for the current block header hash and Cache and then resumes mining. This architecture, including the lazy evaluation mining algorithm, is described in detail below.

\begin{figure}[h]
\centering
\includegraphics[width=230px,keepaspectratio]{Hybrid-Miner.pdf}
\caption{WebEth Architecture}
\label{fig:hybridArchitecture}
\end{figure}

\subsection{Lazy Evaluation}
The mining itself (Step 3) in \verb|WebEth| is based on a lazy evaluation to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers. Specifically, as soon as each browser connects to the webserver, the server sends to the browser the current block header hash and the Cache. Once the browser receives the Cache, it allocates an array buffer to store the DAG nodes.

Once the buffer is allocated, the browser can start iterating over nonces to compute hashes.  
Since, to begin with, the browser does not store any nodes of the DAG, it must compute each node on the fly using the Cache. However, every node that the browser computes is stored in the buffer, for quicker access in the future. Hence, as time passes, the buffer starts filling up, such that more and more nodes are quickly accessed from the buffer rather than being computed from the ground-up, which makes hash computations faster with time. This has the effect that the longer the user remains on the web-page, the better the hash rate gets for that user.

\subsection{Implementation}

The \verb|WebEth| architecture is centered around a central node and client-side Ethereum miners.
